A non-additive generalization of probability theory \\for quantum mechanics and beyond

### 2025-08-05 Articles/2024-NonAdditiveProbability/NonAdditiveProbability.tex
NonAdditiveProbability: fixed caption

			% inscribed tetrahedron
			\begin{scope}[scale=3, every node/.style={font=\small}]
				\coordinate (A) at (0, 1, 0);
				\coordinate (B) at (0, -1/3, {sqrt(8/9)});
				\coordinate (C) at ({sqrt(2/3)}, -1/3, {-sqrt(2/9)});
				\coordinate (D) at ({-sqrt(2/3)}, -1/3, {-sqrt(2/9)});
				\draw (A) -- (B) -- (C) -- cycle;
				\draw (A) -- (B) -- (D) -- cycle;
				\draw (A) -- (C) -- (D) -- cycle;
				\draw (B) -- (C) -- (D) -- cycle;
			\end{scope}
		\end{tikzpicture}
		\caption{}
	\end{subfigure}
	\caption{(a) Example of a SIC-POVM on a Bloch ball. The four extreme points of the tetrahedron represent the states $P_i$. States with positive $\lambda_i$ lie within the tetrahedron, while all other states require negative coefficients. (b) The Bloch ball can alternatively be circumscribed by a larger tetrahedron to guarantee positive coefficients, but the extreme points are no longer physical states.}
\end{figure}

>>>>

			% inscribed tetrahedron
			\begin{scope}[scale=3, every node/.style={font=\small}]
				\coordinate (A) at (0, 1, 0);
				\coordinate (B) at (0, -1/3, {sqrt(8/9)});
				\coordinate (C) at ({sqrt(2/3)}, -1/3, {-sqrt(2/9)});
				\coordinate (D) at ({-sqrt(2/3)}, -1/3, {-sqrt(2/9)});
				\draw (A) -- (B) -- (C) -- cycle;
				\draw (A) -- (B) -- (D) -- cycle;
				\draw (A) -- (C) -- (D) -- cycle;
				\draw (B) -- (C) -- (D) -- cycle;
			\end{scope}
		\end{tikzpicture}
		\caption{}
	\end{subfigure}
	\caption{(a) Example of a SIC-POVM on a Bloch ball. The four extreme points of the tetrahedron represent the states $P_i$. States with positive $\lambda_i$ lie within the tetrahedron, while all other states require negative coefficients. (b) The Bloch ball can alternatively be inscribed within a larger tetrahedron to guarantee positive coefficients, but the extreme points are no longer physical states.}
\end{figure}
